Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-23 supplement.tex
Updates from ShareLaTeX

To illustrate the efficiency and practical feasibility of our Boltzmann sampling approach, we show the distributions of run times for generating 1000 samples (over the Modena benchmark instances and grouped by benchmark sub-set). Since producing a controlled Boltzmann sampling requires significant pre-computation, it is informative to separately show construction and sampling times (Figure~\ref{fig:run-times-redprint}).

\todo[inline]{@Stefan: could you please include technical data about the machines used for the timings? Please also check the claims/statements in the text for correctness. If necessary---please edit.}

@@

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets}
  \caption{\todo[inline]{caption Stefan?}}
  \label{fig:run-times-redprint}
\end{figure}
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{\todo[inline]{caption Stefan?}}
  \label{fig:run-times-rbp}
\end{figure}

>>>>

To illustrate the efficiency and practical feasibility of our Boltzmann sampling approach, we show the distributions of run times (Intel(R) Core(TM) i7-4770 CPU) for generating 20.000 samples (over the Modena benchmark instances and grouped by benchmark sub-set). Since producing a controlled Boltzmann sampling requires significant pre-computation, it is informative to separately show construction and sampling times (Figure~\ref{fig:run-times-redprint}).

@@

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets}\\
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_bp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_bp}
  \caption{\todo[inline]{caption Stefan?}}
  \label{fig:run-times-redprint}
\end{figure}
\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/construction_time_sets_rbp}\quad%
  \includegraphics[width=0.45\textwidth]{Figs/RunTimes/sample_time_sets_rbp}
  \caption{\todo[inline]{caption Stefan?}}
  \label{fig:run-times-rbp}
\end{figure}
